### 2021-08-13 sections/healthcare_application/main.tex
Add info about asymmetric replicator dynamics

The system defined in section [ ] 
% TODO: Reference appropriate section
can be directly applied to a healthcare scenario.
The two queueing systems can be thought of as two Emergency Departments (ED) and 
the distributor as the Emergency Medical Services (EMS) that distributes 
individuals to them.
These individuals are patients of the corresponding Emergency Department 
that are sent to.

The parameters of the model described in section [ ]
% TODO: Reference appropriate section
can also be mapped into parameters of the ED and the EMS.

\begin{itemize}
    \item \( \lambda_2 \): The rate of patients that the EMS receives
    \item \( \lambda_{1_i} \): The arrival rate of other patients to ED \(i\)
    \item \( \mu_i \): The service rate of patients the ED \(i\)
    \item \( C_i \): The number of available resources in ED \(i\)  
    \item \( T_i \): The strategy that ED \(i\) chooses to play
    \item \( N_i \): The patient capacity of ED \(i\)
    \item \( M_i \): The parking capacity of ED \(i\)
    \item \( R \): The time target for both EDs
    \item \( \alpha \in [0, 1] \) : \textit{Importance} of blocking time and lost 
    individuals (equation \ref{eq:obj-distributor})
\end{itemize}

@@

The game to be played now is between the two EDs and the EMS. 
The strategies of the two EDs are the range of thresholds that they can choose
from and their utilities is the proportion of individuals whose time in the 
system lie within a predetermined target time.
The EMS has to decide how to distribute its patients among the two EDs so that 
the blocking time of ambulances is minimised. 
Note that the formulated game here assumes that prior to making a choice the 
EMS knows the strategies that each ED is playing.

% TODO: Add a figure to show the applied game

@@

This subsection aims to analyse how the gaming framework can affect the 
performance measures of the queueing systems and how to escape certain 
inefficient situations.
To study such effects a new concept is introduced that considers the ratio 
between the best possible performance measure and the one that is being
played by the players.
This new concept is defined as the compartmentalised price of anarchy of the 
players of the game and is defined as \(PoA_i(P, s)\), where \(i \in [1, 2]\) 
to distinguish among the two players, \(P\) denotes the performance measure 
function to be used and \(s\) is the strategy that is being played by player 
\( i \). 
The compartmentalised price of anarchy aims to measure inefficiencies in the 
model.
For instance the \(PoA\) for the blocking time of player \(i\) is given by:

\begin{equation}\label{eq:poa_compartmentalised}
    % TODO: Make sure this equation makes sense
    PoA_{i}(B, s) = \frac{B_i(s)}{\min_{\bar{s} \in S_i} B_i(\bar{s})}
\end{equation}

% TODO: Remove \newpage from here
\newpage
Consider a game with the following parameters:

@@

Using equation (\ref{eq:poa_compartmentalised}) and asymmetric replicator 
dynamics (described in section [ ])
% TODO: reference asymmetric replicator dynamics
the game can be simulated and show the compartmentalised price of 
anarchy at every iteration for each ED.
Figure \ref{fig:ard_original} shows the strategies that are being played and 
the values of \(PoA_1(B, s)\) and \(PoA_2(B, s)\) for all iterations of the 
learning algorithm until it reaches an evolutionary stable pair of strategies.

>>>>

The system defined in section \ref{sec:model_overview} can be directly applied 
to a healthcare scenario with two such queueing systems.
The two queueing systems can be thought of as two Emergency Departments (ED) and 
the Emergency Medical Services (EMS) as a distributor that distributes 
patients to them.
The parameters of the model can also be mapped into parameters of the ED and 
the EMS.

\begin{itemize}
    \item \( \lambda_2 \): The rate of non-emergency patients that the EMS 
    receives
    \item \( \lambda_{1_i} \): The arrival rate of other patients to ED \(i\)
    \item \( \mu_i \): The service rate of patients at ED \(i\)
    \item \( C_i \): The number of available resources (beds) in ED \(i\)  
    \item \( T_i \): The strategy that ED \(i\) chooses to play
    \item \( N_i \): The total patient capacity of ED \(i\)
    \item \( M_i \): The total parking capacity of ED \(i\)
    \item \( R \): The time target for both EDs
    \item \( \alpha \in [0, 1] \) : \textit{Importance} of blocking time and 
    lost individuals (equation \ref{eq:obj-distributor})
\end{itemize}

@@

The game to be played now is between the two EDs and the EMS. 
The strategies of the two EDs are the range of thresholds that they can choose
from and their utilities is the proportion of individuals whose time in the 
system lie within a predetermined target time.
The EMS has to decide how to distribute its patients among the two EDs so that 
the blocking time of ambulances is minimised. 
As defined in \ref{sec:model_overview}, the interaction between the two EDs 
is a Normal form game that is then used to inform the decision of the EMS.
Note that the formulated game here assumes that prior to making a choice the 
EMS knows the strategies that each ED is playing (figure 
\ref{fig:imperfect-info-game}).

@@

This subsection aims to analyse how the gaming framework can affect the 
performance measures of the two hospitals and how to avoid certain inefficient 
situations.

In order to analyse the strategies played by the two EDs, the learning algorithm
asymmetric replicator dynamics is used.
% TODO: Cite asymmetric replicator dynamics
The use of a learning algorithm allows to investigate, not only the outcome of 
the game, but also how that outcome is reached.
Consider figure \ref{fig:ard-by-itself}. 
By running asymmetric replicator dynamics on the system the behaviour that 
emerges can be observed.
It can be seen that for these particular set of parameters 
(\ref{eq:ard-parameters}), the strategies of the two hospitals converge over 
time. 
Both hospital 1 (row player) and hospital 2 (column player) seem to be playing 
the same strategy \(s_10\) which indicates that thresholds \(T_1 = 10\) and 
\(T_2 = 10\) are played.
What is more important in this example is how the two hospitals reached these
decisions which also highlights the importance of using a learning algorithm.
Hospital 2 is able to reach the decision in a very short time while hospital 1
takes longer to get there.

\begin{figure}[H]
    \centering
    \includegraphics[scale=0.4, trim=120 0 120 0]{imgs/asymmetric_rd/asymmetric_rd.png}
    \label{fig:ard-by-itself}
    \caption{Asymmetric replicator dynamics run}
\end{figure}

\begin{multicols}{3}
    \begin{itemize} \label{eq:ard-parameters}
        \item \( \lambda_{1_1} \) = 1
        \item \( \mu_1 \) = 2
        \item \( C_1 \) = 2
        \item \( N_1 \) = 10
        \item \( M_1 \) = 6

        \columnbreak
        \item \( \lambda_{1_2} \) = 2
        \item \( \mu_2 \) = 2.5
        \item \( C_2 \) = 2
        \item \( N_2 \) = 10
        \item \( M_2 \) = 6

        \columnbreak
        \item \( \lambda_2 \) = 2
        \item \( R \) = 2
        \item \( \alpha \) = 0.5
    \end{itemize}
\end{multicols}

To study such effects a new concept is introduced that considers the ratio 
between each hospital's best achievable blocking time and the one that is being
played.
This new concept is defined as the compartmentalised price of anarchy of the 
players of the game and is defined as \(PoA_i(\tilde{s})\), where 
\(i \in [1, 2]\) to distinguish among the two players/hospitals where 
\(\tilde{s}\) is the strategy that is being played by player \( i \). 
The compartmentalised price of anarchy aims to measure inefficiencies in the 
model.
The \(PoA\) for the blocking time of player \(i\) for strategy \(\tilde{s}\) 
is given by:

\begin{equation}\label{eq:poa_compartmentalised}
    PoA_{i}(\tilde{s}) = \frac{B_i(\tilde{s})}{\min_{s \in S_i} B_i(s)}
\end{equation}

Consider a game with the following parameters:

@@

Using equation (\ref{eq:poa_compartmentalised}) and asymmetric replicator 
dynamics the game can be simulated and show the compartmentalised price of 
anarchy at every iteration for both players.
Figure \ref{fig:ard_original} shows the strategies that are being played and 
the values of \(PoA_1(s)\) and \(PoA_2(s)\) for all iterations of the 
learning algorithm until it reaches an evolutionary stable pair of strategies.
